### 2014-06-30 Quality_Reports/PCR_bottleneck.Rmd
Added observations on figure 1

```{r PBC_fun,include = TRUE,results = "hide",echo = TRUE}
PBC <- function(file)
{
  require(GenomicAlignments)
  rr = readGAlignmentsFromBam(file,param = NULL)
  ss1 = subset(rr,subset =strand(rr)=="+")
  ss2 = subset(rr,subset = strand(rr)=="-")
  N11 = length(unique(start(ss1)))
  N12 = length(unique(end(ss2)))
  N1 = N11+N12
  Nd1 = length(ss1)
  Nd2 = length(ss2)
  Nd = Nd1 + Nd2
  PBC1 = round(N11 / Nd1,4)
  PBC2 = round(N12 / Nd2,4)
  PBC = round(N1 /Nd,4)
  return(c(PBC_plus=PBC1,PBC_minus=PBC2,PBC=PBC))  
}
```
### Results

And the following results where obtained:
```{r load_data,include = FALSE,echo = TRUE,results = "hide"}
load("../RData/PBC.RData")
tab = list()
tab[[1]] = as.data.frame(t(do.call(cbind,SET)))
tab[[1]]$type = "ChIP-Seq.SET"
tab[[2]] = as.data.frame(t(do.call(cbind,PET)))
tab[[2]]$type = "ChIP-Seq.PET"
tab[[3]] = as.data.frame(t(do.call(cbind,EXO)))
tab[[3]]$type = "ChIP-Exo"
```
### Figures
```{r overall_boxplot,include = TRUE,echo = FALSE,results = "hide",fig.height = 4,fig.width = 4}
df = do.call(rbind,tab)
p <- ggplot(df,aes(factor(type),PBC))+geom_boxplot(aes(fill = factor(type)))
print(p)
```

>>>>

```{r PBC_fun,include = TRUE,results = "hide",echo = TRUE}
PBC <- function(file)
{
  require(GenomicAlignments)
  rr = readGAlignmentsFromBam(file,param = NULL)
  ss1 = subset(rr,subset =strand(rr)=="+")
  ss2 = subset(rr,subset = strand(rr)=="-")
  N11 = length(unique(start(ss1)))
  N12 = length(unique(end(ss2)))
  N1 = N11+N12
  Nd1 = length(ss1)
  Nd2 = length(ss2)
  Nd = Nd1 + Nd2
  PBC1 = round(N11 / Nd1,4)
  PBC2 = round(N12 / Nd2,4)
  PBC = round(N1 /Nd,4)
  return(c(PBC_plus=PBC1,PBC_minus=PBC2,PBC=PBC))  
}
```

```{r load_data,include = FALSE,echo = TRUE,results = "hide"}
load("../RData/PBC.RData")
tab = list()
tab[[1]] = as.data.frame(t(do.call(cbind,SET)))
tab[[1]]$type = "ChIP-Seq.SET"
tab[[2]] = as.data.frame(t(do.call(cbind,PET)))
tab[[2]]$type = "ChIP-Seq.PET"
tab[[3]] = as.data.frame(t(do.call(cbind,EXO)))
tab[[3]]$type = "ChIP-Exo"
```
### Figures

**Figure 1**
```{r overall_boxplot,include = TRUE,echo = FALSE,results = "hide",fig.height = 4,fig.width = 4}
df = do.call(rbind,tab)
df$type = factor(df$type)
p <- ggplot(df,aes(type,PBC))+geom_boxplot(aes(fill = type))+
   theme(legend.position = "none",axis.text.x = element_text(angle = 90))
print(p)
```
Some observations on the figure:
- The overall level of the ChIP-Exo's PBC coefficients is lower than the level of the other two ChIP-Seq labels
- The range of the ChIP-Exo's PBC coefficients is also smaller than other two ranges. In particular, the range of the PET coefficients is smaller than the range of the SET coefficients.
